\section*{Abstract}
% Ising model is a relatively new model used to determine magnetic properties of materials and objects. In this work we study properties of Ising model on ensembles of conformations. Conformation is a random walk on a regular grid which can represent a molecule. Structure of the conformation depends on the temperature. And other studies have shown that conformations have a geometric phase transition. Two states of conformation at low and high temperatures are called globule and coil respectively. Geometrically globule and coil conformations are similar to one and two dimensional grids. As most vertices in globules have 4 neighbors and in coils they mostly have 2. It was proven that on a one-dimensional grid Ising model has no magnetic phase transition. But on a two-dimensional grid phase transition exists. Our hypothesis is that globular conformations have magnetic phase transition. The goal of this research is to determine the magnetic phase transition point in globular conformations and compare it to the point of geometric phase transition in conformations.


This paper studies magnetic properties of the Ising model on ensembles of conformations.
This work focuses on the relationship between the structural properties of conformations and the magnetic properties of the Ising model built on conformations. In particular, the effect of a geometric phase transition on the appearance of a magnetic transition. Since at low temperatures the structure of conformations is similar to a two-dimensional lattice, and it is known that the Ising model on a two-dimensional lattice has a phase transition. And at high temperatures, the conformations are similar to a one-dimensional lattice, on which there is no transition in the Ising model.
In other works in this field, the spin subsystem of the Ising model and the conformation structure change simultaneously, but this considers a model with frozen disorder. Thus, in our model, the conformation is first generated, and then the Ising model is considered with a fixed geometry.
The results of the work are: the magnetic properties of conformations in each of the phases, the magnetic transition point in the globular phase, the change in the magnetic properties of conformations during a geometric phase transition, the influence of structural features of conformations on their magnetic properties.